% Resumo em língua estrangeira (em inglês Abstract, em espanhol Resumen, em francês Résumé)
\begin{center}
	{\Large{\textbf{Twydi: A tool for Documentation for Software Development Teams}}}
\end{center}

\vspace{1cm}

\begin{flushright}
	Author: Igo Marques da Silva\\
	Advisor: Prof. Dr. Fernando Marques Figueira Filho
\end{flushright}

\vspace{1cm}

\begin{center}
	\Large{\textsc{\textbf{Abstract}}}
\end{center}

\noindent The Software development process is extremely complex, involving many roles in a team to achieve the desired product. Frequently, developers show a fall on their productivity due to external factors or even because of the way the project is going on. It is needed to find a new way to breed motivation on each member of the team, and identify goals to be achieved.

\noindent
This work presents a tool that, mining software repositories, allows to visualize the best members of the team based on their contribution, being it pull requests, issues, or even comments on those activities. All of it in a gamified way, using badges. In doing so it will be able to build motivation in each member allied to a healthy competitiveness on the team, as allows each developer to realize which points he stands out and which points he should improve himself. The work doesn't use chat data yet, although it would be a good way to improve the data that are already used and give a more accurate analysis of the team situation.

\noindent\textit{Keywords}: Software repositories mining. Gamification. Software Development.
